Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-09-19 ms.tex
More edits.

This paper is organized as followed.  In $\S\ref{sec:model}$ we describe our model, including the sample of galaxies used in our analysis ($\S\ref{sec:sample}$) and our numerical procedure for calculating the steady-state hydrodynamic profile of the CNM ($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our results.  In $\S\ref{sec:applications}$ we describe applicaiton of our results, including a comparison of our gas profiles to those inferred from {\it Chandra} observations and to the measured $L_X-\Mbh$ relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In $\S\ref{sec:summary}$ we summarize our results.

\section{Model}
\label{sec:model}

@@

Given $I(\xi)$ we follow the procedure outlined by \citetalias{WangMerritt:2004a} to compute the spherically-symmetric stellar density profile $\rhostar(r)$ and stellar mass profile $M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in our model.  For reference, note that stellar density $\rhostar\sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r \gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while $\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the SMBH mass $\Mbh$ is determined from.... ({\bf BDM: more info!}).

@@

Rewriting equation (\ref{eq:mdot_gas}) as
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}} =\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
\end{align}
we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
\begin{align}
  \rs=\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}}\frac{v_{w}^{2}}{v_{w,0}^{2}},
  \label{eq:rs_simple}
\end{align}
where in the second line we have used the fact that $v_{w}^{2}/2 =
c_s^2/(\gamma-1)$ at $\rs$ ({\bf BDM: Check - as this depends on
  whether eq 10 is correct}).  Thus, provided that a stagnation radius
exists which is interior to the sphere of influence radius, the
accretion rate predicted by our model is quite close to $\dot{M}_{\rm
  B}$.

@@

Figure~\ref{fig:profiles} shows three representative profiles of the
density $\rho(r)$, temperature $T(r)$, and radial velocity $v(r)$, as
well as the cumulative X-ray luminosity.  As expected, the gas density
increases towards the SMBH, with a characteristic radial slope $\rho
\propto r^{n}$ with $n \approx 1$ near the stagnation radius (marked
as a square in Fig.~\ref{fig:profiles}. The gas density The
temperature profile is relatively flat at large radii, but increases
as $\propto 1/r$ interior to the sphere of influence, both behaviors
expected for virialized gas in near hydrostatic equilibrium.  The
inwardly directed velocity increases towards the hole approaching the
expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
interior to the sonic point, and then increases outwards towards large
radii. {\bf BDM: I made this up - in general we need more explanation
  of what the plots are actually showing, with some physical
  explanation.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), velocity  ({\it bottom}), and
    interior X-ray luminosity ({\it bottom}), calculated for three
    characteristic galaxies from our samples: NGC1172 ({\it blue}),
    NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line
    styles denote different values of the effective wind heating rate,
    $v_{w,0}$=1000 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
     dot-dashed}).}
\end{figure}

@@

subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.

Though representing a much smaller quantity of mass, main sequence winds have much higher velocities and hence contribute a disproportionally large share of the kinetic energy of winds.  \citep{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim 100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old stellar population.  On the other hand, for a very young stellar population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind heating from massive stars can be much greater, $\gtrsim 10^{3}$ km s$^{-1}$.  In Appendix C we present a toy model for how $v_{\rm w,0}$ varies as a function of stellar age.

@@

However, SNe can only be approximated as constant source of heating throughout space and time if the rate of SNe is rapid compared to the inflow time at the radius of interest (\citealt{ShcherbakovWong+:2014a}).  To estimate when this approximation is valid, we estimate the ``Ia radius" 
\begin{eqnarray}
r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \approx 40\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{-1/2} \; {\rm pc} \sim 43 M_{\bullet,8}^{0.1}\,{\rm pc}
\label{eq:rIa}
\end{eqnarray}
as the location exterior of which the time interval between subsequent supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old stellar population and in the final equality we estimate the velocity dispersion using the $M_{\bullet}-\sigma$ relationship (equation~[\ref{eq:Msigma}]).

@@

We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase increase with SMBH mass $M_{\bullet}$.  This appears to be in contradiction with the general down sizing trend observed for SMBH accretion in the local universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the fact that for quiescent galaxies the nuclear X-ray luminosity obeys $L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$ \citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot \sim
\Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x \sim \Mbh^{1.5-2}$, steeper than the observed relationship. (If $L_x \sim \Mdot^2$ the discrepance becomes worse).  One possible solution that the wind mass loss rate $\eta$ decreases with $\Mbh$, as would be expected if low mass SMBH preferentially hosted younger stellar populations.  Another possible explanation, which we favor, is that the effective heating rate of the CNM $v_{\rm w,0}$ decreases with decreasing SMBH mass.  This could again be due to a young stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating sources such as SN Ia and millisecond pulsars, or it could be due to the fact that Ia occur too infrequently inside the stagnation radius for low mass black holes.

@@

Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.  We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.  The results of this exercise are presented in Figure~\ref{fig:allen_compare}.

@@

\subsubsection{Comparison with observed X-ray Luminosity-Mass
  Relation}
%Note currently I reverse-engineer the stellar mass from the black
%hole mass inferred from M-sigma; however, it would be better to use
%the tabulated black hole mass from the Mbh-Mbulge relation.
Figure 1 of \citealt{MillerGallo+:2014a} plots the observed
relationship of unresolved x-ray luminosity versus galactic stellar
mass for a sample of quiescent galaxies. We may construct a similar
relationship with our own sample using the inferred accretion rates
from our solutions.  To infer an x-ray luminosity for each solution,
we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
10^{-7}$, which gives comparable an x-ray luminosities comparable to
those in \citealt{MillerGallo+:2014a}.
%describe the quadratic procedure.

Our results are plotted in Figure~\ref{fig:bh_xray}. For each galaxy
in our sample we select the $\vwO$=200 km/s if $\rs<\rIa$
for this solution,  $\vwO$=500 km/s is $\rs>\rIa$ for this solution,
or exclude it.  $\vwO$ encapsulates heating SNe Ia heating, and it
would only make sense to include this heating if $\rs$>$\rIa$ as
discussed in Section~\ref{sec:heating}. At low $\Mbh$ we have
$\vwO$=200 km/s and at high $\Mbh$ we have $\vwO$=500 km/s.
Note that much of our sample is excluded in this Figure, since for
$\vwO$=200 km/s we would have $\rs>\rIa$ and four $\vwO$=500 km/s we
would have $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$
would be inconsistent with the assumed level of heating).

\begin{figure}
\includegraphics[width=\columnwidth]{bh_xray.eps}
\caption{\label{fig:bh_xray} Accretion power plotted as a function of 
  stellar mass for our solutions (points) with the trend of nuclear
  x-ray luminosity with stellar mass and the detection upper limit
  from Figure 1 of \citealt{MillerGallo+:2014a}. In the top panel we
  take the accretion power to be $\epsilon \Mdot c^2$, with
  $\epsilon=5\time 10^{-7}$ chosen to make our accretion powers
  comparable to the observed x-ray luminosities..}
\end{figure}

@@

Figure~\ref{fig:cooling} shows H/C as a function of radius for all of our solutions, with different colors denoting different values of $v_{w,0}$.  For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.  With a few exceptions this is also true for $\vwO$=500 km s$^{-1}$.  However, for our lowest heating rate $\vwO$=200 km s$^{-1}$ cooling may be quite important, especially for high $\eta$ (young stellar population;  Appendix~\ref{app:eta}).

@@

  The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
  $\rsoi$. %%AG-Need to explain this somehow.
  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Figure 2 of
  \citet{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
  of radius for a sample of early type galaxies. On scales of $\sim 0.1
  R_e$ $\lambda_R$ is either less than 0.1 or rapidly declining for most
  of their sample %%need to be clearer on rapidly declining also compare
  %% this scale to the sphere of influence scale.
  This suggests that angular momentum should generally be unimportant.

  \section{Summary and conclusions}
  We have calculated steady-state models for circumnuclear medium of a
  sample of early type galaxies, assuming that gas is supplied
  entirely by stellar wind mass loss and heated by shocked stellar
  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
  with $\Mbh$. We may then compare our results with observed trends of
  nuclear x-ray luminosity. Our main conclusions may be summarized as
  follows.

  \begin{enumerate}
    \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value
      of $\alpha$ depends on the slope of the stellar density profile
      ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively).

  \end{enumerate}

>>>>

This paper is organized as followed.  In $\S\ref{sec:model}$ we
describe our model, including the sample of galaxies used in our
analysis ($\S\ref{sec:sample}$) and our numerical procedure for
calculating the steady-state hydrodynamic profile of the CNM
($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
results.  In $\S\ref{sec:applications}$ we describe applicaiton of our
results, including a comparison of our gas profiles to those inferred
from {\it Chandra} observations and to the measured $L_X-\Mbh$
relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
$\S\ref{sec:summary}$ we summarize our results.
\section{Model}
\label{sec:model}

@@

Given $I(\xi)$ we follow the procedure outlined by
\citetalias{WangMerritt:2004a} to compute the spherically-symmetric
stellar density profile $\rhostar(r)$ and stellar mass profile
$M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
our model.  For reference, note that stellar density $\rhostar\sim
r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
\gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
$\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
%%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
%%calculated from an outdated M-sigma. It would be bizarre to use 2
%%different relations.

@@

Rewriting equation (\ref{eq:mdot_gas}) as
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}} =\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
\end{align}
we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
\begin{align}
  \rs=\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}}\frac{v_{w}^{2}}{v_{w,0}^{2}},
  \label{eq:rs_simple}
\end{align}
where in the second line we have used the fact that $v_{w}^{2}/2 =
c_s^2/(\gamma-1)$ at $\rs$.  Thus, provided that a stagnation radius
exists which is interior to the sphere of influence radius, the
accretion rate predicted by our model is quite close to $\dot{M}_{\rm
  B}$.
 %({\bf BDM: Check - as this depends on
 % whether eq 10 is correct})

@@

Figure~\ref{fig:profiles} shows three representative profiles of the
density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.
As expected, the gas density increases towards the SMBH.  For some
profiles (e.g. NGC1172 and NGC4478) the density $\rho$ follows a power
law from the stagnation radius (squares in Fig.~\ref{fig:profiles})
inwards $\rho \propto r^{n}$ with $n \approx 1$. Note that this is
shallower than the $-3/2$ for Bondi accretion. However, the power law
behavior does not extend through all radii. NGC4365 which has a
prominent break in the gas density profile, near the stagnation
radius. This is also roughly the location of the break in the stellar
light profile ($\rb$). The temperature profile is relatively flat at
large radii, but increases as $\propto 1/r^{k}$ interior to the sphere
of influence, where $k$ is smaller than 1 (which would be expected for
virialized gas).  The inwardly directed velocity increases towards the
hole approaching the expected free-fall rate $v \propto v_{\rm
  ff}\propto r^{-1/2}$ interior to the sonic point, and then increases
outwards towards large radii.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...
% AG -- I am somewhat concerned about boundary effects in
% NGC3115. Perhaps the break in the gas density profile is due to
% boundary effects--I know that in this case the break is not
% associated with a break in the stellar density profile

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), velocity  ({\it bottom}), and
    interior X-ray luminosity ({\it bottom}), calculated for three
    characteristic galaxies from our samples: NGC1172 ({\it blue}),
    NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line
    styles denote different values of the effective wind heating rate,
    $v_{w,0}$=500 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
     dot-dashed}).}
\end{figure}

@@

\subsubsection{Stellar winds} Although most of the mass supplied to
the CNM by stellar winds occurs during the giant AGB phase, these
winds represent a negligible heating source compared to the random
wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is
much less than the stellar potential $\sigma$.

Though representing a much smaller quantity of mass, main sequence
winds have much higher velocities and hence contribute a
disproportionally large share of the kinetic energy of winds.
\citep{NaimanSoares-Furtado+:2013a} estimate that $v_{\rm w,0} \sim
100-150$ km s$^{-1}$ for main sequence winds assuming a relatively old
stellar population.  On the other hand, for a very young stellar
population of age $t_{\star} \lesssim 10^{7}$ yrs the effective wind
heating from massive stars can be much greater, $\gtrsim 10^{3}$ km
s$^{-1}$.  
%In Appendix C we present a toy model for how $v_{\rm w,0}$
%varies as a function of stellar age.
%AG-Appendix C is not written! As this draft will be circulated I
%don't want references to things which do not exist!

@@

However, SNe can only be approximated as constant source of heating
throughout space and time if the rate of SNe is rapid compared to the
inflow time at the radius of interest
(\citealt{ShcherbakovWong+:2014a}).  To estimate when this
approximation is valid, we estimate the ``Ia radius"
\begin{align}
r_{\rm Ia} \sim \left(\frac{G}{R_{\rm Ia}\sigma}\right)^{1/2} \approx
&40\left(\frac{\sigma}{200\,{\rm km\,s^{-1}}}\right)^{-1/2} \; {\rm pc}\sim 43 M_{\bullet,8}^{0.1}\,{\rm pc} 
\label{eq:rIa}
\end{align}
as the location exterior of which the time interval between subsequent
supernovae $\tau_{\rm Ia} \sim 1/M_{\rm enc}R_{\rm Ia} \sim
G/r\sigma^{2}R_{\rm Ia}$ exceeds the local dynamical timescale $t_{\rm
  dyn} \sim r/\sigma$, where we again adopt the Ia rate for an old
stellar population and in the final equality we estimate the velocity
dispersion using the $M_{\bullet}-\sigma$ relationship
(equation~[\ref{eq:Msigma}]).

@@

We find that $\dot{M}/\dot{M}_{\rm edd}$ tends to increase with SMBH
mass $M_{\bullet}$.  This appears to be in contradiction with the
general down sizing trend observed for SMBH accretion in the local
universe (e.g.~\citealt{Heckman+04}; \citealt{Gallo+08}), such as the
fact that for quiescent galaxies the nuclear X-ray luminosity obeys
$L_X \sim \Mbh^\alpha$, where $\alpha\simeq 0.7-0.8$
\citep{MillerGallo+:2014a}.  Our model instead predicts that $\Mdot
\sim \Mbh^{1.5-2}$, such that if $L_x\sim M$, then we would have $\L_x
\sim \Mbh^{1.5-2}$, steeper than the observed relationship.

This is shown in the top panel Figure~\ref{fig:bh_xray}. The
relationship from \citealt{MillerGallo+:2014a} and their detection
upper limits are shown as the blue and black solid lines
respectively. The points correspond to the $\dot{M} c^2$ for our
solutions (scaled by $5\times 10^{-7}$).  We must choose a $\vwO$ for
each galaxy.  We select $\vwO$=200 km/s if $\rs<\rIa$ for this $\vwO$,
$\vwO$=500 km/s if $\rs>\rIa$ for this $\vwO$, or exclude it. If
$L_x \sim \Mdot^2$ the discrepancy becomes worse, as shown in the
bottom panel of Fig.~\ref{fig:bh_xray}, where we plot $2 \times
10^{-4} (\eddr) \Mdot c^2$ from our solutions with the relation from
\citealt{MillerGallo+:2014a}.

One possible solution that the wind mass loss rate $\eta$ decreases
with $\Mbh$, as would be expected if low mass SMBH preferentially
hosted older stellar populations.  Another possible explanation is
that the effective heating rate of the CNM $v_{\rm w,0}$ decreases
with decreasing SMBH mass.  This could again be due to an older
stellar population, since $v_{w,0} \propto \eta^{-1/2}$ for heating
sources such as SN Ia and millisecond pulsars.
%, or it could be due to the fact that Ia occur too infrequently inside
%the stagnation radius for low mass black holes.
%AG-We now think that SNe Ia would become important only at the
%highest values of Mbh.
%AG-Note sure where the best place for this discussion would
%be--here or after presenting the comparisons with Miller et al.

@@

Five of the galaxies in the \citet{AllenDunn+:2006a} sample overlap with that in \citetalias{WangMerritt:2004a}.  We may thus compare our results for the $T$ and $\rho$ profiles with those inferred from observations for the overlapping galaxies.  The results of this exercise are presented in Fig.~\ref{fig:allen_compare}.

@@

% \subsubsection{Comparison with observed X-ray Luminosity-Mass
%   Relation}
% %Note currently I reverse-engineer the stellar mass from the black
% %hole mass inferred from M-sigma; however, it would be better to use
% %the tabulated black hole mass from the Mbh-Mbulge relation.
% Fig. 1 of \citealt{MillerGallo+:2014a} plots the observed
% relationship of unresolved x-ray luminosity versus galactic stellar
% mass for a sample of quiescent galaxies. We may construct a similar
% relationship with our own sample using the inferred accretion rates
% from our solutions.  To infer an x-ray luminosity for each solution,
% we scale our calculated $\Mdot c^2$ by a constant. We pick $5\times
% 10^{-7}$, which gives x-ray luminosities comparable to
% those in \citealt{MillerGallo+:2014a}. We also try an alternate
% prescription in which $L_x$ is quadratic in $\Mdot$. In particular, we
% take $L_x=2 \times 10^{-4} (\eddr) \Mdot c^2$.

% We must make choose a $\vwO$ for each galaxy.  We select $\vwO$=200
% km/s if $\rs<\rIa$ for this solution, $\vwO$=500 km/s if $\rs>\rIa$
% for this solution, or exclude it.  At low $\Mbh$ we have $\vwO$=200
% km/s and at high $\Mbh$ we have $\vwO$=500 km/s.  Note that much of
% our sample is excluded in this Fig., since for $\vwO$=200 km/s we
% would have $\rs>\rIa$ and four $\vwO$=500 km/s we would have
% $\rs<\rIa$ (i.e. the relative locations of $\rs$ and $\rIa$ would be
% inconsistent with the assumed level of heating).

% %AG-power law may be closer to 1.4 & 1.8 than to 1.5 & 2.
% Our results are plotted in Fig.~\ref{fig:bh_xray}. In our model
% there is a steeper dependence $\Mbh$ on $M_{\rm gal}$ than in
% \citealt{MillerGallo+:2014a}. We find $L_x \propto M_{\rm gal}^{1.5}$ when
% $L_x \propto M_{\rm gal}^{2}$, whereas \citealt{MillerGallo+:2014a} finds
% that $L_x \propto M_{\rm gal}^{0.7-0.8}$.

\begin{figure}
\includegraphics[width=\columnwidth]{bh_xray.eps}
\caption{\label{fig:bh_xray} Accretion power plotted as a function of
  stellar mass for our solutions (points) and the trend of nuclear
  x-ray luminosity with stellar mass (black line) and the detection
  upper limit (blue line) from Fig. 1 of
  \citealt{MillerGallo+:2014a}. In the top panel we take the accretion
  power to be $\epsilon_1 \Mdot c^2$, with $\epsilon_1=5\times
  10^{-7}$ chosen to make our accretion powers comparable to the
  observed x-ray luminosities. In the bottom panel, we take the
  accretion power to be quadratic in $\Mdot$--$\epsilon_2 \eddr \Mdot
  c^2$ with $\epsilon2$=$2\times10^{-4}$. For a given galaxy, we take
  either $\vwO=200$ km/s (green points) or $\vwO=500$ km/s (orange
  points). We choose the solution for which the relative positions of
  $\rs$ and $\rIa$ are consistent with the assumed level of heating}
  %(see text for details).}
\end{figure}

@@

Fig.~\ref{fig:cooling} shows H/C as a function of radius for all of our solutions, with different colors denoting different values of $v_{w,0}$.  For our highest heating rates we observe that cooling is unimportant for all solutions across all radii.  With a few exceptions this is also true for $\vwO$=500 km s$^{-1}$.  However, for our lowest heating rate $\vwO$=200 km s$^{-1}$ cooling may be quite important, especially for high $\eta$ (young stellar population;  Appendix~\ref{app:eta}).

@@

  The inner sonic point, $\rss$ general occurs at $\simeq 1\%$ of
  $\rsoi$. %%AG-Need to explain this somehow.
  So if $\lambdars\lsim 0.1$, $\rcirc<\rss$. In Fig. 2 of
  \citet{EmsellemCappellari+:2007a} $\lambda_R$ is plotted as function
  of radius for a sample of early type galaxies. On scales of $\sim 0.1
  R_e$ $\lambda_R$ is either less than 0.1 or rapidly declining for most
  of their sample %%need to be clearer on rapidly declining also compare
  %% this scale to the sphere of influence scale.
  This suggests that angular momentum should generally be unimportant.

  \section{Summary and conclusions}
  \label{sec:summary}
  We have calculated steady-state models for circumnuclear medium of a
  sample of early type galaxies, assuming that gas is supplied
  entirely by stellar wind mass loss and heated by shocked stellar
  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
  with $\Mbh$. We may then compare our results with observed trends of
  nuclear x-ray luminosity. Our main conclusions may be summarized as
  follows.

  \begin{enumerate}
  \item We find that $\eddr \propto \Mbh^{\alpha}$, where the value of
    $\alpha$ depends on the slope of the stellar density profile
    ($\alpha\simeq0.5,1$ for cusp and core galaxies respectively). One
    possible solution that the wind mass loss rate (i.e. $\eta$)
    decreases with $\Mbh$, as would be expected if low mass SMBH
    preferentially hosted older stellar populations. Another possible
    explanation is that the effective heating rate of the CNM $v_{\rm w,0}$
    decreases with decreasing SMBH mass. This could again be due to an
    older stellar population, since $v_{\rm w,0} \propto \eta^{−1/2}$
    for heating sources such as SN Ia and millisecond pulsars.
  \item We compare the $\Mdot$ for each of our solution to the one
    calculated from the Bondi formula. We find that they generally to
    a factor of a few. In our model the accretion rate is determined
    from the gas properties at the stagnation radius, $\rs$, which
    agrees with the Bondi radius, $\rb$, within a factor of a
    few. Thus, use of the Bondi formula is a good approximation.
  \item We compare our solutions for density and temperature to those
    inferred from Chandra x-ray observations by \citealt{Allen+:2006a}
    and \citealt{RussellMcNamara+:2013a} for a handful of galaxies in
    which our sample overlap with theirs. In general, we cannot match
    the observed gas density slope on large scales. 
  \end{enumerate}
